---
title: "simulation_MG1_800G"
output:
  pdf_document: default
  html_document: default
date: "2024-11-29"
---

```{r include=FALSE}
library(ggplot2)
library(igraph)
library(stringr)
library(simmer)
library(tidyverse)
library(readr)
library(SciViews)
library(dplyr)
library(viridis)
library(readxl)
library(openxlsx)
```



```{r}
source("func/igraph_functions.R")
source("func/general_function_base.R")
source("func/simmer_function_base.R")
```
#Input data

The **average packet size** is taken from: Amsterdam Internet Exchange Ethernet Frame Size Distribution, statistics available online at https://stats.ams-ix.net/sflow/size.html, accessed on July 2023

Packet sizes in Bytes: 64-127, 128-511, 512 - 1023, 1024 - 1513, 1514, more than 1515.


With their probabilities: 0.332, 0.054, 0.033, 0.037, 0.346, 0.146, 0.052
```{r}
PS_size=c((64+127)/2,(128+255)/2,(256+511)/2, (512+1023)/2, (1024+1513)/2, 1514, (1515+9100)/2)
PS_weights=c(33.2/100, 5.4/100, 3.3/100, 3.7/100, 34.6/100, 14.6/100, 5.2/100)
N = sum(PS_size*PS_weights)
N
var_N <- sum(PS_size^2*PS_weights) - N^2
Cs2 <- var_N/(N^2)

CapacityGbps = 800
#Calculation of delays for different capacities
Load_local = 0.3
Load_regional = 0.5
Load_national = 0.4
```

Input excel file with topology information: links, nodes, traffic

Prefix base - the common name for the nodes in the file.
```{r}
#topology_choice <- readline(prompt = "Enter 'Tokyo' or 'Milano' to choose the respective topology: ")

# # Define the file paths based on user input
file_name_v2 <- "input_files/Metro_topology_full_Tokyo.xlsx"
prefix_base <- "Tokyo_"
topology_name = "Tokyo"
print(file_name_v2)

# file_name_v2 <- "input_files/Metro_topology_full_Milano.xlsx"
# prefix_base <- "Node"
# topology_name = "Milano"
# print(file_name_v2)
# 
# file_name_v2 <- "input_files/Metro_topology_MAN157.xlsx"
# prefix_base <- ""
# topology_name = "MAN157"
# print(file_name_v2)


```

```{r}
nodes_info <- read_excel(file_name_v2, sheet = 1)
links_info <- read_excel(file_name_v2, sheet = 2)
traffic_file <- read_excel(file_name_v2, sheet = 3)
```

```{r}
print(links_info)
print(nodes_info)
print(traffic_file)
```
Definition of national and regional Cental Offices (COs).
```{r}
national_nodes <- c()
regional_nodes <- c()

for (i in seq_along(nodes_info$node_code)) {
  if (nodes_info$node_code[i] == "HL2") {
    national_nodes <- c(national_nodes, i)
  }
  if (nodes_info$node_code[i] == "HL3") {
    regional_nodes <- c(regional_nodes, i)
  }
}

cat("National nodes:", national_nodes, "\n")
cat("Regional nodes:", regional_nodes, "\n")
```

# Functions
### Vysochanskij–Petunin's bound calculation function
Inputs:
- **delay_hops**: Vector of delay at each hop
- **a**: Upper bound percentile from 0 to 1

Output:
- Vysochanskij–Petunin's upper bound

```{r}
func_bounds_VP <- function(delay_hops, a)
{
  mu = sum(delay_hops)
  sigma = sqrt(sum(delay_hops^2))
  k <- sqrt(4/9/(1-a))
  Prop_VP <- 1 - 4/9/(k^2)
  upper_bound_VP <- k * sigma + mu
  return(upper_bound_VP)
}
```

##Simmer simulation


<!-- ### Function to perform simulation in a simmer environment with M/G/1 queueing model -->
<!-- Inputs: -->
<!-- - **env**: Simmer environment -->
<!-- - **from**: Source node -->
<!-- - **to**: Destination node -->
<!-- - **graph**: Graph object representing the network topology -->
<!-- - **traffic_val**: Traffic value (lambda) for the simulation -->
<!-- - **log_info**: Information for logging purposes -->
<!-- - **PS_size**: Packet size -->
<!-- - **PS_weights**: Packet weights -->

<!-- Output: -->
<!-- - List containing updated environment, trajectory name, transmission delay, and propagation delay -->

```{r include=FALSE}
simmer_simulation_mg1 <- function(env, from, to, graph, traffic_val, log_info, PS_size, PS_weights)
{
  name = paste0('traffic_', from, "_", to, "_", log_info)
  if (from != to && traffic_val != 0) {
    c(traffic, delay_transm, delay_prop) := simmer_trajectory_simulation_mg1(env, from, to, trajectory_name = traffic , graph, log_info, PS_size = PS_size, PS_weights = PS_weights) #creating trajectory
    assign(name, traffic)
    print(name)
    #print(get(name))
    env<- simmer_generator(env, get(name), name, traffic_val)
  }
  return(list(env, name, delay_transm, delay_prop))
}
```

<!-- ### Function to create cross trajectories in the simmer environment based on the network load -->
<!-- Inputs: -->
<!-- - **env**: Simmer environment -->
<!-- - **g**: Graph object representing the network topology -->
<!-- - **from**: Source node -->
<!-- - **to**: Destination node -->
<!-- - **lambda_simmer**: Traffic value (lambda) for the simulation -->
<!-- - **PS_size**: Packet size -->
<!-- - **PS_weights**: Packet weights -->

<!-- Output: -->
<!-- - Updated simmer environment -->
```{r include=FALSE}
simmer_crosstrajectory_simulation_mg1 <- function(env, g, from, to, lambda_simmer, PS_size, PS_weights)
{
  path <- shortest_paths(g, from, to, weights = NULL, output = "both", algorithm = c("automatic"))
  N = sum(PS_size*PS_weights)
  path_size <- length(path[["vpath"]][[1]])
  nodes_capacity <- rep(0, length(V(g)))
  nodes_capacity[path[["vpath"]][[1]][-path_size]] <- E(g)$capacityGbps[path[["epath"]][[1]]]
  nodes_capacity_Bps <- nodes_capacity*1e9
  nodes_capacity <- nodes_capacity_Bps/(8*N)

  nodes_load <- rep(0, length(V(g)))
  nodes_load[path[["vpath"]][[1]][-path_size]] <- E(g)$Load[path[["epath"]][[1]]]

  for (i in path[["vpath"]][[1]][-path_size])
  {

    load_compare <- lambda_simmer/(nodes_capacity[i])
    if (nodes_load[i] > load_compare )
    {
      print(paste0("node_", i))
      print(nodes_capacity[i])
      print(nodes_load[i])
      trajectory_name <- trajectory() %>%
        seize(paste0("node_", i)) %>%
        set_attribute("capacity", nodes_capacity_Bps[i]) %>%
        timeout(function() 8*sample(PS_size,size = 1, replace = T, prob = PS_weights)/(get_attribute(env, "capacity"))) %>%
        release(paste0("node_", i)) #%>%

      name <- paste0("traffic_cross_", from,"_", to, "_node_", i,"_")
      assign(name, trajectory_name)
      traffic_val <- nodes_load[i] * nodes_capacity[i] - lambda_simmer
      print(traffic_val)
      print(lambda_simmer)
      print(nodes_load[i]*nodes_capacity[i])
      env<- simmer_generator(env, get(name), name, traffic_val)
    }
  }
  return(env)
}


```
<!-- ### Main function to perform simulation using trajectories in a simmer environment -->
<!-- Inputs: -->
<!-- - **g**: Graph object representing the network topology -->
<!-- - **traffic_file**: Data frame containing traffic information -->
<!-- - **PS_size**: Packet size -->
<!-- - **PS_weights**: Packet weights -->
<!-- - **load**: Traffic load (default: $0.3$) -->
<!-- - **CapacityGbps**: Link capacity in Gbps (default: $10~Gb/s$) -->

<!-- Output: -->
<!-- - List containing delay and traffic information -->

```{r include=FALSE}
simulation_simmer <- function(g, traffic_file, PS_size, PS_weights, load = 0.3, CapacityGbps = 10){
  E(g)$Queue_Delay_sim <- 0
  E(g)$Queue_Delay_theor_VP_upbound99 <- 0
  E(g)$Queue_Delay_sim_99p <- 0

  #####################################simmer
  queue_delay_tr_flow <- c()
  prop_delay_tr_flow <- c()
  delay_tr_flow <- c()
  delay_tr_flow_p_99 <- c()
  exp_delay_igraph <- c()
  delay_tr_flow_VP_upbound_p_99_100 <- c()
  digits = 10
  print("start simulation in simmer")
  N = sum(PS_size*PS_weights)
  cat("Load = ",load, "\n")
  traffic_file$traffic_ps <- CapacityGbps*1e9/(8*N)*load
  traffic_file$trafficGbps <- CapacityGbps*load
  assign("traffic_file", traffic_file, .GlobalEnv)
  for (line in 1:nrow(traffic_file))
  {
    print(line)
    #env <- simmer("SuperDuperSim") #creating the simmer environment

    if(traffic_file$sourceID[line] != traffic_file$destinationID[line] && traffic_file$traffic_ps[line] != 0)
    {
      env <- simmer()
      lambda_simmer <- traffic_file$traffic_ps[line]
      set.seed(42)
      env <- simmer_resources(g, env) # add resources for all nodes of igraph (func is in the file simmer_fictions)
      env <- simmer_crosstrajectory_simulation_mg1(env, g, traffic_file$sourceID[line], traffic_file$destinationID[line], lambda_simmer, PS_size = PS_size, PS_weights = PS_weights) #creating cross trajectories with theirs generator  (func is in the file simmer_fictions)
      c(env, traffic_traj_name, delay_queue, delay_prop) := simmer_simulation_mg1(env, traffic_file$sourceID[line], traffic_file$destinationID[line], g, traffic_val=lambda_simmer, log_info = "", PS_size = PS_size, PS_weights = PS_weights) #creation main trajectory with its generator

      env %>% #env execution
        run(10000/lambda_simmer) #10000 packets of the main lambda trajectory


      #########################delay results processing
      all_arrivals_res <- data.frame(env %>%
                                       get_mon_arrivals(per_resource = TRUE) %>%
                                       transform(waiting_time_in_queue = round(end_time - start_time - activity_time)) %>%
                                       transform(spending_time = end_time - start_time))


      ############################plots for each node (only with queuing delay)
      ##########computing the bounds and parameters (mean, variance, and etc)
      path <- shortest_paths(g, traffic_file$sourceID[line], traffic_file$destinationID[line] ,weights = NULL, output = "both", algorithm = c("automatic"))
      path_size <- length(path[["vpath"]][[1]])
      n=1
      for (node in path[["vpath"]][[1]][-path_size])
      {
        traffic <- dplyr::filter(all_arrivals_res, paste0("node_", node) == all_arrivals_res$resource)
        if (length(traffic$spending_time) != 0)
        {
          print(node)
          delay_nodes <- mean(traffic$spending_time)
          p_99_result <- unname(quantile(traffic$spending_time, probs = 0.99))
          ####################
          print(paste("Node - ", node, ":"))
          bounds_function_node(delay_queue[node], traffic$spending_time, digits, info = paste("Node - ", node, ";","For the traffic flow:from",traffic_file$sourceID[line],"to", traffic_file$destinationID[line]))#plot the results for each node
          E(g)[get.edge.ids(g, c(path[["vpath"]][[1]][n],path[["vpath"]][[1]][n+1]))]$Queue_Delay_sim <- delay_nodes
          E(g)[get.edge.ids(g, c(path[["vpath"]][[1]][n],path[["vpath"]][[1]][n+1]))]$Queue_Delay_sim_99p <- p_99_result
          E(g)[get.edge.ids(g, c(path[["vpath"]][[1]][n],path[["vpath"]][[1]][n+1]))]$Queue_Delay_theor_VP99 <- func_bounds_VP(delay_queue[node], 0.99)

          print(E(g)[get.edge.ids(g, c(path[["vpath"]][[1]][n],path[["vpath"]][[1]][n+1]))])
          n=n+1

        }

      }

      ###########################plots for each traffic flow (prop + queuing delays)
      #########################delay results processing
      all_arrivals_res <- data.frame(env %>%
                                       get_mon_arrivals(per_resource = FALSE) %>%
                                       transform(waiting_time_in_queue = round(end_time - start_time - activity_time)) %>%
                                       transform(spending_time = end_time - start_time))
      traffic <- dplyr::filter(all_arrivals_res, grepl(traffic_traj_name , all_arrivals_res$name))
      exp_delay = sum(delay_prop,delay_queue)
      exp_delay_igraph <- append(exp_delay_igraph,exp_delay)

      bounds_function_1w_path(sum(delay_prop), sum(delay_queue), traffic$spending_time, digits, info = paste("For the traffic flow:from",traffic_file$sourceID[line],"to", traffic_file$destinationID[line]))#plot the results for tr flow
      queue_delay_tr_flow <- append(queue_delay_tr_flow, sum(delay_queue))
      prop_delay_tr_flow <- append(prop_delay_tr_flow, sum(delay_prop))
      delay_tr_flow <- append(delay_tr_flow, mean(traffic$spending_time))
      delay_tr_flow_p_99 <- append(delay_tr_flow_p_99, unname(quantile(traffic$spending_time, probs = 0.99)))
      VP_upbound <- func_bounds_VP(delay_queue, 0.99) + sum(delay_prop)
      delay_tr_flow_VP_upbound_p_99_100 <- append(delay_tr_flow_VP_upbound_p_99_100, VP_upbound)

    } else{
      print("no info of traffic")
      exp_delay_igraph <- append(exp_delay_igraph,0)
      queue_delay_tr_flow <- append(queue_delay_tr_flow, 0)
      prop_delay_tr_flow <- append(prop_delay_tr_flow, NaN)
      delay_tr_flow <- append(delay_tr_flow, 0)
      delay_tr_flow_p_99 <- append(delay_tr_flow_p_99, 0)
      delay_tr_flow_VP_upbound_p_99_100 <- append(delay_tr_flow_VP_upbound_p_99_100, 0)
      print(delay_tr_flow)
    }
  }


  igraph_df_calc <- data_frame(exp_delay_igraph, delay_tr_flow, delay_tr_flow_p_99, delay_tr_flow_VP_upbound_p_99_100)

  assign("igraph_df_calc", igraph_df_calc, .GlobalEnv)

  return(list(delay_tr_flow, exp_delay_igraph, delay_tr_flow_p_99, delay_tr_flow_VP_upbound_p_99_100, g))
}

```

<!-- ### Function to calculate end-to-end delays theoretically -->
<!-- Inputs: -->
<!-- - **g**: Graph object representing the network topology -->
<!-- - **traffic_file**: Data frame containing traffic information -->
<!-- - **Cs2**: coefficient of variation of service time -->

<!-- Output: -->
<!-- - List containing updated graph and theoretical delay values -->

```{r include=FALSE}
prop_queue_tr_delay_e2e <- function(g, traffic_file, Cs2){

  E(g)$Queue_Delay <- ifelse(E(g)$Traffic == 0, 0, E(g)$Load/(1-E(g)$Load)/E(g)$Traffic*(Cs2 + 1)/2) #M/G/1
  latencyPropTransQueuing_theor_s <- rep(0, nrow(traffic_file))
  latencyPercentile99_theor_s <- rep(0, nrow(traffic_file))
  for (line in 1:nrow(traffic_file))
  {
    if(traffic_file$traffic_ps[line] != 0){
      vertex_sourse <- which(V(g)$name==traffic_file$sourceID[line])
      vertex_destination<- which(V(g)$name==traffic_file$destinationID[line])
      path <- shortest_paths(g, vertex_sourse, vertex_destination,
                             weights = NULL,
                             output = "both",
                             algorithm = c("automatic"))
      latencyPropTransQueuing_theor_s[line] = sum(E(g)[path[["epath"]][[1]]]$Queue_Delay) + sum(E(g)[path[["epath"]][[1]]]$Prop_Delay)
      latencyPercentile99_theor_s[line] <- func_bounds_VP(E(g)[path[["epath"]][[1]]]$Queue_Delay, 0.99) + sum(E(g)[path[["epath"]][[1]]]$Prop_Delay)
    }
    else {
      latencyPropTransQueuing_theor_s[line] <- 0
      latencyPercentile99_theor_s[line] <- 0
    }
  }
  return(list(g, latencyPropTransQueuing_theor_s, latencyPercentile99_theor_s))
}

```
## Igraph calculations
<!-- ### Main function to perform simulation using theoretical delay calculations -->
<!-- Inputs: -->
<!-- - **nodes_info**: Information about nodes in the network -->
<!-- - **links_info**: Information about links in the network -->
<!-- - **traffic_file**: Data frame containing traffic information -->
<!-- - **Capacity**: Link capacity in Gbps (default: $10~Gb/s$) -->
<!-- - **calc_dist**: Flag to calculate distance (default: $FALSE$) -->
<!-- - **distance**: Custom distance parameter (default: $5$) -->
<!-- - **Load_local**: Local traffic load (default: $0.3$) -->
<!-- - **Load_regional**: Regional traffic load (default: $0.5$) -->
<!-- - **Load_national**: National traffic load (default: $0.4$) -->
<!-- - **prefix_base**: Base prefix for nodes -->
<!-- - **national_nodes**: List of national nodes -->
<!-- - **regional_nodes**: List of regional nodes -->
<!-- - **N**: Number of packets -->
<!-- - **Cs2**: coefficient of variation of service time -->

<!-- Output: -->
<!-- - List containing updated graph and delay information -->
```{r include=FALSE}
simulation_igraph <- function(nodes_info, links_info, traffic_file, Capacity = 10, calc_dist =  FALSE, distance = 5, Load_local = 0.3, Load_regional = 0.5, Load_national = 0.4, prefix_base, national_nodes, regional_nodes, N, Cs2){

  traffic_file$traffic_ps <- traffic_file$trafficGbps*10^9/(8*N)
  g = graph_from_data_frame(links_info, directed = TRUE)
  E(g)$capacityGbps <- Capacity
  for (NCO in national_nodes){
    a <- (filter(traffic_file, traffic_file$destinationID == V(g)$name[NCO]))
    size <- length(a$destinationID)
    E(g)$capacityGbps[incident(g, NCO, mode = c("in"))] <- Capacity*size
  }
  E(g)$Capacity <- E(g)$capacityGbps*1e9/(8*N) #p/s
  ############distance put original distance(calc_dist = 1) or custom distance (calc_dist = 1) with paramentr "distance" in km
  if( calc_dist == TRUE ) {
    E(g)$Distance = E(g)$distanceKm * distance
  }
  else {
    E(g)$Distance <- E(g)$distanceKm
  }
  ####Load of the links
  #for Local CO
  E(g)$Load <- Load_local
  #national COs
  for (NCO in national_nodes){
    E(g)$Load[incident(g, NCO, mode = c("in"))] <- Load_national
  }
  #regional COs
  for (RCO in regional_nodes){
    E(g)$Load[incident(g, RCO, mode = c("in"))] <- Load_regional
  }

  E(g)$Traffic <- E(g)$Capacity * E(g)$Load
  E(g)$Ni = E(g)$Load/(1-E(g)$Load) # average number of packets in each system
  E(g)$Prop_Delay <- 5*10^(-6)*E(g)$Distance
  c(g, traffic_file$latencyPropTransQueuing_theor_s_mg1, traffic_file$latencyPercentile99_theor_s_mg1) := prop_queue_tr_delay_e2e(g, traffic_file, Cs2)

  data_av <- traffic_file$latencyPropTransQueuing_theor_s_mg1
  data_99 <- traffic_file$latencyPercentile99_theor_s_mg1


  assign("traffic_file", traffic_file, .GlobalEnv)

  links_info$prop_delay_s <- 5*10^(-6)*links_info$distanceKm
  assign("links_info_df", links_info, .GlobalEnv)

  #removing the local traffic
  data_av <- data_av[data_av != 0]
  data_99 <- data_99[data_99 != 0]
  trafficGbps <- E(g)$Capacity * E(g)$Load[E(g)$Capacity * E(g)$Load != 0]/1e9*(8*N) #Gbps
  return(list(g, data_av, data_99, trafficGbps))

}

```

## Building the graph:

```{r}
g <- graph_from_data_frame(links_info, directed = TRUE, vertices = nodes_info)
```
## Calculations of the capacity in p/s
```{r}
E(g)$Distance <- E(g)$distanceKm
E(g)$Definition <- paste0(as_edgelist(g)[,1],"->",as_edgelist(g)[,2])
E(g)$Capacity <- E(g)$capacityGbps*10^9/(8*N)

```


## Plot graph

```{r}
#plot graph
V(g)$color <- "tomato"
V(g)$color[national_nodes] <- "yellow"

deg <- degree(g, mode="all")
V(g)$size <- deg*1.5
l <- layout_nicely(g)
plot(g, edge.arrow.size=.3, vertex.label = V(g)$name, edge.curved=.5, layout=l)

```
#Igraph calculations
## Total traffic calculatons
## Calculations of the load, average number of packets, queueing and propagation delays:
Load for Local COs $0.3$;
Regional COs $0.5$;
Rational COs $0.4$

```{r}
c(g_c10, data_av, data_99) := simulation_igraph(nodes_info, links_info, traffic_file, Capacity = 10, calc_dist = 1, distance = 0.5, Load_local, Load_regional, Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
```

#Simmer simulation
Including queuing, transmission, propagation delay
Output table with links information

Simulation of all traffic flows, comparision of experimental with theretical


```{r include=FALSE}
c(traffic_file$Delay_sim_s, traffic_file$Delay_th_s, traffic_file$D99_sim_s, traffic_file$VPbound_99th_s, g_c10) := simulation_simmer(g_c10, traffic_file, PS_size, PS_weights, load = 0.3, CapacityGbps = CapacityGbps)
traffic_file_v2 <- dplyr::filter(traffic_file, VPbound_99th_s != 0)

```
#Results
```{r}
links_info_df
```
```{r}
traffic_file_v2
```
#Calculation of delays for different capacities

```{r}
capacities = c(400, 800, 1200, 1600, 3200)
c(g_c400_dg_l05, data_av_c400_dg_l05, data_99_c400_dg_l05, trafficGbps_c400_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[1], calc_dist = 0, distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
c(g_c800_dg_l05, data_av_c800_dg_l05, data_99_c800_dg_l05, trafficGbps_c800_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[2], calc_dist = 0,  distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
c(g_c12_dg_l05, data_av_c12_dg_l05, data_99_c12_dg_l05, trafficGbps_c12_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[3], calc_dist = 0,  distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
c(g_c16_dg_l05, data_av_c16_dg_l05, data_99_c16_dg_l05, trafficGbps_c16_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[4], calc_dist = 0,  distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)

c(g_c32_dg_l05, data_av_c32_dg_l05, data_99_c32_dg_l05, trafficGbps_c32_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[5], calc_dist = 0,  distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)

```

```{r}
text_size = 12

# Boxplot for trafficGbps (bit rate in Gbps)
df_plot_traffic <- data.frame(capacity = c(
                                            rep("400G", length(trafficGbps_c400_dg_l05)),
                                            rep("800G", length(trafficGbps_c800_dg_l05)),
                                            rep("1200G", length(trafficGbps_c12_dg_l05)),
                                            rep("1600G", length(trafficGbps_c16_dg_l05)),
                                            rep("3200G", length(trafficGbps_c32_dg_l05))),
                              value = c(trafficGbps_c400_dg_l05,
                                        trafficGbps_c800_dg_l05,
                                        trafficGbps_c12_dg_l05,
                                        trafficGbps_c16_dg_l05,
                                        trafficGbps_c32_dg_l05),
                              type_of_calc = "bit rate",
                              city = c(rep(topology_name,length(trafficGbps_c32_dg_l05)*10)))

ggplot(df_plot_traffic, aes(x = fct_reorder(capacity, value, .desc = TRUE), y = value, fill = type_of_calc)) +
  geom_boxplot() +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    legend.position = c(0.8, 0.99),
    axis.title.y = element_text(size = text_size),
    axis.title.x = element_text(size = text_size),
    legend.text = element_text(size = text_size),
    legend.background = element_rect(colour = "black"),
    axis.text = element_text(size = text_size),
    strip.text = element_text(size = text_size)
  ) +
  facet_grid(. ~ city ) +
  ylab("Bit rate, Gbps") +
  xlab("Capacity, Gbps")

```

```{r echo=FALSE}
#Boxplots

df_plot_capacity <- data.frame(capacity = c(
                                            rep("400G", length(data_av_c400_dg_l05)),
                                            rep("800G", length(data_av_c400_dg_l05)),
                                            rep("1200G", length(data_av_c400_dg_l05)),
                                            rep("1600G", length(data_av_c400_dg_l05)),
                                            rep("3200G", length(data_av_c400_dg_l05)),
                                            rep("400G", length(data_av_c400_dg_l05)),
                                            rep("800G", length(data_av_c400_dg_l05)),
                                            rep("1200G", length(data_av_c400_dg_l05)),
                                            rep("1600G", length(data_av_c400_dg_l05)),
                                            rep("3200G", length(data_av_c400_dg_l05))),
                               value = c(data_99_c400_dg_l05,
                                         data_99_c800_dg_l05,
                                         data_99_c12_dg_l05,
                                         data_99_c16_dg_l05,
                                         data_99_c32_dg_l05,
                                         data_av_c400_dg_l05,
                                         data_av_c800_dg_l05,
                                         data_av_c12_dg_l05,
                                         data_av_c16_dg_l05,
                                         data_av_c32_dg_l05
                                         ),
                               type_of_calc = c(rep("Vysochanskij–Petunin 99th",length(data_av_c400_dg_l05)*5),
                                                rep("average delay",length(data_av_c400_dg_l05)*5)),
                               city = c(rep(topology_name,length(data_av_c400_dg_l05)*10)))

# Calculate the mean N values for each capacity group
N_means <- c(mean(data_99_c400_dg_l05)/mean(data_av_c400_dg_l05),
             mean(data_99_c800_dg_l05)/mean(data_av_c800_dg_l05),
             mean(data_99_c12_dg_l05)/mean(data_av_c12_dg_l05),
             mean(data_99_c16_dg_l05)/mean(data_av_c16_dg_l05),
             mean(data_99_c32_dg_l05)/mean(data_av_c32_dg_l05))
N_means_y <- c(max(data_99_c400_dg_l05),
               max(data_99_c800_dg_l05),
               max(data_99_c12_dg_l05),
               max(data_99_c16_dg_l05),
               max(data_99_c32_dg_l05))

text_size = 12
# Grouped boxplot
ggplot(df_plot_capacity, aes(x = fct_reorder(capacity, value, .desc = TRUE), y = value * 1000000, fill = type_of_calc)) +
  geom_boxplot() +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    legend.position = c(0.8, 0.99),
    axis.title.y = element_text(size = text_size),
    axis.title.x = element_text(size = text_size),
    legend.text = element_text(size = text_size),
    legend.background = element_rect(colour = "black"),
    axis.text = element_text(size = text_size),
    strip.text = element_text(size = text_size)
  ) +
  facet_grid(. ~ city ) +
  ylab("Delay, us") +
  xlab("Capacity, Gbps") +
  annotate("text", x = c(1,2,3,4,5), y = N_means_y*1e6 - 1,
           label = paste0(round(N_means, 3), "x"), vjust = -0.5, size = text_size/2.5)
```
As shown in the plot, the queuing delay does not significantly affect the e2e delay. This is because it is too low compared to the propagation delay and does not result in noticeable changes for changing capacity higher than 800G.



#Calculation of delays for different distances
```{r}
#Calculation of delays for different distances
c(g_c100_d05g_l05, data_av_c100_d05g_l05, data_99_c100_d05g_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = 800, calc_dist = 1, distance = 0.5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)

#Calculation of delays for different distances
c(g_c100_dg_l05, data_av_c100_dg_l05, data_99_c100_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = 800, calc_dist = 1, distance = 1, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)

c(g_c100_d2g_l05, data_av_c100_d2g_l05, data_99_c100_d2g_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = 800, calc_dist = 1, distance = 2, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
c(g_c100_d4g_l05, data_av_c100_d4g_l05, data_99_c100_d4g_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = 800, calc_dist = 1, distance = 4, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
c(g_c100_d10g_l05, data_av_c100_d10g_l05, data_99_c100_d10g_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = 800, calc_dist = 1, distance = 10, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
```

```{r echo=FALSE}
diam_km <-  round(diameter(g_c100_d05g_l05, directed = TRUE, unconnected = TRUE, weights = E(g_c100_d05g_l05)$Distance), digits = 2)
av_link_km <- round(mean(E(g_c100_d05g_l05)$Distance), digits = 2)
name_05 <- paste0("0.5x\n", "Diam = ", diam_km, "km\n av_link_dist", " = ", av_link_km, "km")
name_1 <- paste("1x\n", "Diam = ", round(diameter(g_c100_dg_l05, directed = TRUE, unconnected = TRUE, weights = E(g_c100_dg_l05)$Distance), digits = 2), "km\nav_link_dist = ", round(mean(E(g_c100_dg_l05)$Distance), digits = 2), "km")
name_2 <- paste("2x\n", "Diam = ", round(diameter(g_c100_d2g_l05, directed = TRUE, unconnected = TRUE, weights = E(g_c100_d2g_l05)$Distance), digits = 2), "km\nav_link_dist = ", round(mean(E(g_c100_d2g_l05)$Distance), digits = 2), "km")
name_4 <- paste("4x\n", "Diam = ", round(diameter(g_c100_d4g_l05, directed = TRUE, unconnected = TRUE, weights = E(g_c100_d4g_l05)$Distance), digits = 2), "km\nav_link_dist = ", round(mean(E(g_c100_d4g_l05)$Distance), digits = 2), "km")
name_10 <- paste("10x\n", "Diam = ", round(diameter(g_c100_d10g_l05, directed = TRUE, unconnected = TRUE, weights = E(g_c100_d10g_l05)$Distance), digits = 2), "km\nav_link_dist = ", round(mean(E(g_c100_d10g_l05)$Distance), digits = 2), "km")

####distanceVSdelay
distance = c(
             rep(name_1, length(data_99_c100_dg_l05)),
             rep(name_2, length(data_99_c100_d2g_l05)),
             rep(name_4, length(data_99_c100_d4g_l05)),
             rep(name_10, length(data_99_c100_d10g_l05)),
             rep(name_1, length(data_av_c100_dg_l05)),
             rep(name_2, length(data_av_c100_d2g_l05)),
             rep(name_4, length(data_av_c100_d4g_l05)),
             rep(name_10, length(data_av_c100_d10g_l05))
  )

type_of_calc = c(rep("Vysochanskij–Petunin 99th",length(distance)/2),
                 rep("average delay",length(distance)/2))

paste("0.5x", "diam", diam_km, "km av link dist", av_link_km, "km")
value = c(
  data_99_c100_dg_l05,
  data_99_c100_d2g_l05,
  data_99_c100_d4g_l05,
  data_99_c100_d10g_l05,
  data_av_c100_dg_l05,
  data_av_c100_d2g_l05,
  data_av_c100_d4g_l05,
  data_av_c100_d10g_l05
  )

df_plot_dist <- data.frame(distance, value, type_of_calc, city = c(rep(topology_name,length(type_of_calc))))

N_means_delay <- c(
  mean(data_99_c100_dg_l05) / mean(data_av_c100_dg_l05),
  mean(data_99_c100_d2g_l05) / mean(data_av_c100_d2g_l05),
  mean(data_99_c100_d4g_l05) / mean(data_av_c100_d4g_l05),
  mean(data_99_c100_d10g_l05) / mean(data_av_c100_d10g_l05)
)

N_means_delay_y <- c(
  max(data_99_c100_dg_l05) ,
  max(data_99_c100_d2g_l05),
  max(data_99_c100_d4g_l05),
  max(data_99_c100_d10g_l05)
)

df_plot_dist$distance <- factor(df_plot_dist$distance, levels = c(name_1, name_2, name_4, name_10))

text_size = 12
# grouped df_plot_dist
ggplot(df_plot_dist, aes(x=distance, y=value*1000000, fill=type_of_calc)) +
  geom_boxplot()+
  theme_gray() +
  theme(
     legend.title = element_blank(), legend.position = c(0.25, 0.85),
     axis.title.y = element_text(size = text_size),
     axis.title.x = element_text(size = text_size),
     legend.text = element_text(size = text_size),
     strip.text = element_text(size = text_size)
   ) +
  facet_grid(.~city)+
  ylab("Delay, us") +
  xlab("Link distance") +
  annotate("text", x = c(1,2,3,4), y = N_means_delay_y*1e6-3,
           label = paste0(round(N_means_delay, 3), "x"), vjust = -0.5, size = text_size/2)


```
```{r}

prop_queue_tr_delay_e2e <- function(g, traffic_file, Cs2){

  E(g)$Queue_Delay <- ifelse(E(g)$Traffic == 0, 0, E(g)$Load/(1-E(g)$Load)/E(g)$Traffic*(Cs2 + 1)/2) #M/G/1
  latencyPropTransQueuing_theor_s <- rep(0, nrow(traffic_file))
  latencyPercentile99_theor_s <- rep(0, nrow(traffic_file))
  
  latencyProp_s <- rep(0, nrow(traffic_file))
  latencyPercentile99_theor_TransQueuing_s <- rep(0, nrow(traffic_file))
  processing_FEC_s <- rep(0, nrow(traffic_file))
  
  for (line in 1:nrow(traffic_file))
  {
    if(traffic_file$traffic_ps[line] != 0){
      vertex_sourse <- which(V(g)$name==traffic_file$sourceID[line])
      vertex_destination<- which(V(g)$name==traffic_file$destinationID[line])
      path <- shortest_paths(g, vertex_sourse, vertex_destination,
                             weights = NULL,
                             output = "both",
                             algorithm = c("automatic"))
      latencyPropTransQueuing_theor_s[line] = sum(E(g)[path[["epath"]][[1]]]$Queue_Delay) + sum(E(g)[path[["epath"]][[1]]]$Prop_Delay)
      latencyPercentile99_theor_s[line] <- func_bounds_VP(E(g)[path[["epath"]][[1]]]$Queue_Delay, 0.99) + sum(E(g)[path[["epath"]][[1]]]$Prop_Delay)
      
      latencyProp_s[line] = sum(E(g)[path[["epath"]][[1]]]$Prop_Delay)
      latencyPercentile99_theor_TransQueuing_s[line] <- func_bounds_VP(E(g)[path[["epath"]][[1]]]$Queue_Delay, 0.99)
      processing_FEC_s[line] <- 4*1e-6*length(path[["epath"]][[1]])
    }
    else {
      latencyPropTransQueuing_theor_s[line] <- 0
      latencyPercentile99_theor_s[line] <- 0
      latencyProp_s[line] <- 0
      latencyPercentile99_theor_TransQueuing_s[line] <- 0
      processing_FEC_s[line] <- 0

    }
  }
  
  return(list(g, latencyPropTransQueuing_theor_s, latencyPercentile99_theor_s, latencyProp_s, latencyPercentile99_theor_TransQueuing_s, processing_FEC_s))
}


simulation_igraph <- function(nodes_info, links_info, traffic_file, Capacity = 10, calc_dist =  FALSE, distance = 5, Load_local = 0.3, Load_regional = 0.5, Load_national = 0.4, prefix_base, national_nodes, regional_nodes, N, Cs2){

  traffic_file$traffic_ps <- traffic_file$trafficGbps*10^9/(8*N)
  g = graph_from_data_frame(links_info, directed = TRUE)
  E(g)$capacityGbps <- Capacity
  for (NCO in national_nodes){
    a <- (filter(traffic_file, traffic_file$destinationID == V(g)$name[NCO]))
    size <- length(a$destinationID)
    E(g)$capacityGbps[incident(g, NCO, mode = c("in"))] <- Capacity*size
  }
  E(g)$Capacity <- E(g)$capacityGbps*1e9/(8*N) #p/s
  ############distance put original distance(calc_dist = 1) or custom distance (calc_dist = 1) with paramentr "distance" in km
  if( calc_dist == TRUE ) {
    E(g)$Distance = E(g)$distanceKm * distance
  }
  else {
    E(g)$Distance <- E(g)$distanceKm
  }
  ####Load of the links
  #for Local CO
  E(g)$Load <- Load_local
  #national COs
  for (NCO in national_nodes){
    E(g)$Load[incident(g, NCO, mode = c("in"))] <- Load_national
  }
  #regional COs
  for (RCO in regional_nodes){
    E(g)$Load[incident(g, RCO, mode = c("in"))] <- Load_regional
  }

  E(g)$Traffic <- E(g)$Capacity * E(g)$Load
  E(g)$Ni = E(g)$Load/(1-E(g)$Load) # average number of packets in each system
  E(g)$Prop_Delay <- 5*10^(-6)*E(g)$Distance
  c(g, traffic_file$latencyPropTransQueuing_theor_s_mg1, traffic_file$latencyPercentile99_theor_s_mg1, latencyProp_s_mg1, latencyPercentile99_theor_TransQueuing_s_mg1, processing_FEC_s) := prop_queue_tr_delay_e2e(g, traffic_file, Cs2)

  data_prop <- latencyProp_s_mg1
  data_99_TransQueuing <- latencyPercentile99_theor_TransQueuing_s_mg1


  assign("traffic_file", traffic_file, .GlobalEnv)

  links_info$prop_delay_s <- 5*10^(-6)*links_info$distanceKm
  assign("links_info_df", links_info, .GlobalEnv)

  #removing the local traffic
  data_av <- data_av[data_av != 0]
  data_99 <- data_99[data_99 != 0]
  trafficGbps <- E(g)$Capacity * E(g)$Load[E(g)$Capacity * E(g)$Load != 0]/1e9*(8*N) #Gbps
  
  return(list(g, data_prop, data_99_TransQueuing, trafficGbps, processing_FEC_s))
  

}



```


```{r}
capacities = c(400, 800, 1200, 1600, 3200)
c(g_c400_dg_l05, data_prop_c400_dg_l05, data_99_TransQueuing_c400_dg_l05, trafficGbps_c400_dg_l05, processing_FEC_s_c400_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[1], calc_dist = 0, distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
c(g_c800_dg_l05, data_prop_c800_dg_l05, data_99_TransQueuing_c800_dg_l05, trafficGbps_c800_dg_l05, processing_FEC_s_c800_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[2], calc_dist = 0,  distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
c(g_c12_dg_l05, data_prop_c12_dg_l05, data_99_TransQueuing_c12_dg_l05, trafficGbps_c12_dg_l05, processing_FEC_s_c12_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[3], calc_dist = 0,  distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
c(g_c16_dg_l05, data_prop_c16_dg_l05, data_99_TransQueuing_c16_dg_l05, trafficGbps_c16_dg_l05, processing_FEC_s_c16_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[4], calc_dist = 0,  distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)

c(g_c32_dg_l05, data_prop_c32_dg_l05, data_99_TransQueuing_c32_dg_l05, trafficGbps_c32_dg_l05, processing_FEC_s_c32_dg_l05) :=simulation_igraph(nodes_info, links_info, traffic_file, Capacity = capacities[5], calc_dist = 0,  distance = 5, Load_local = Load_local, Load_regional = Load_regional, Load_national = Load_national, prefix_base, national_nodes, regional_nodes , N, Cs2)
```

```{r}
# Create a data frame with mean propagation and queuing delays for each capacity
df_plot_delay <- data.frame(
  capacity = factor(c("400G", "800G", "1200G", "1600G", "3200G"), 
                    levels = c("400G", "800G", "1200G", "1600G", "3200G")),
  delay_type = rep(c("Propagation Delay", "D.99 Queuing Delay", "FEC processing"), each = 5),
  delay_value = c(
    mean(data_prop_c400_dg_l05), mean(data_prop_c800_dg_l05), mean(data_prop_c12_dg_l05), mean(data_prop_c16_dg_l05), mean(data_prop_c32_dg_l05),
    mean(data_99_TransQueuing_c400_dg_l05), mean(data_99_TransQueuing_c800_dg_l05), mean(data_99_TransQueuing_c12_dg_l05), mean(data_99_TransQueuing_c16_dg_l05), mean(data_99_TransQueuing_c32_dg_l05),
    mean(processing_FEC_s_c400_dg_l05), mean(processing_FEC_s_c800_dg_l05), mean(processing_FEC_s_c12_dg_l05), mean(processing_FEC_s_c16_dg_l05), mean(processing_FEC_s_c32_dg_l05)
    
  )
)

# Plot the barplot
ggplot(df_plot_delay, aes(x = capacity, y = delay_value * 1e6, fill = delay_type)) +
  geom_bar(stat = "identity", position = "stack") +
  theme_minimal() +
  labs(
    x = "Capacity (Gbps)",
    y = "Delay (us)",
    fill = "Type of Delay"
  ) +
  scale_fill_manual(values = c("Propagation Delay" = "steelblue", "D.99 Queuing Delay" = "tomato", "FEC processing" = "yellow")) +
  theme(
    text = element_text(size = 12),
    legend.position = "top"
  )

```
```{r}
df_MAN157 = data.frame(prop = c(mean(data_prop_c400_dg_l05), mean(data_prop_c800_dg_l05), mean(data_prop_c12_dg_l05), mean(data_prop_c16_dg_l05), mean(data_prop_c32_dg_l05)), 
                       queuing = c( mean(data_99_TransQueuing_c400_dg_l05), mean(data_99_TransQueuing_c800_dg_l05), mean(data_99_TransQueuing_c12_dg_l05), mean(data_99_TransQueuing_c16_dg_l05), mean(data_99_TransQueuing_c32_dg_l05) ))

```

#Creating the report file
```{r include=FALSE}
update_file <- function(links_info_df, traffic_file, file_name = "Milano_topology_result.xlsx", file_old_name)
{
    wb <- createWorkbook()
    addWorksheet(wb, sheetName = "Nodes")
    writeData(wb, sheet = 1, read_excel(file_old_name, sheet = 1))
    addWorksheet(wb, sheetName = "Links")
    writeData(wb, sheet = 2, links_info_df)
    addWorksheet(wb, sheetName = "Services")
    writeData(wb, sheet = 3, traffic_file)
    saveWorkbook(wb, file_name, overwrite = TRUE)
}



```
```{r}
update_file(links_info_df, traffic_file_v2, file_name = paste0(topology_name, "_topology_result.xlsx"), file_old_name = file_name_v2)

```

